Trends of downward SDR in Thessaloniki 

### 2023-03-05 Article.Rmd
Commit 2023-03-05 09:17

---
title:         "Trends of downward SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisthanasis@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

```{r trackercomm, echo=F, fig.cap="tracker"}
knitr::include_graphics("./images/longtermtrendsALL-2.pdf")
```

>>>>

---
title:         "Trends of downward SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

```{r trackercomm, echo=F, fig.cap="tracker"}
knitr::include_graphics("./images/LongtermTrends-1.pdf")
```
